Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*

### 2019-01-14 analyses/reproduce_analyses.Rmd
remove bootstrap calls for old figures of univariate landscapes.

egglarval_RF_Diam <- bootstrap_fitness(
  logistic_model = egglarval_model,
  newdata = newdata_Diam,
  bootstraps=n_boots_plots)
```

@@

egglarval_RF_Clutch <- bootstrap_fitness(
  logistic_model = egglarval_model,
  newdata = newdata_Clutch,
  bootstraps=n_boots_plots)
```

@@

egglarval_RF_Pref <- bootstrap_fitness(
  logistic_model = egglarval_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)

eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots)

linear_eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = linear_eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots) 
```

>>>>

@@

@@

# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
eggegg_RF_Pref <- bootstrap_fitness(
  logistic_model = eggegg_model, 
  newdata = newdata_Pref,
  bootstraps=n_boots_plots) 
```
